Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-04-25 doc/thesis/appendix.Rnw
Appendix

\begin{figure}
  \centering
  \includegraphics{kernel-I-tree.pdf}
  \caption{
    Transmission trees simulated over \gls{BA} networks with varying values of
    $I$, the number of infected nodes when the epidemic simulation was stopped.
  }
  \label{fig:Itrees}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-m-tree.pdf}
  \caption{
    Transmission trees simulated over \gls{BA} networks with varying values of
    $m$, the number of edges added per vertex.
  }
  \label{fig:mtrees}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-N-tree.pdf}
  \caption{
    Transmission trees simulated over \gls{BA} networks with varying values of
    $N$, the number of nodes in the network.
  }
  \label{fig:Ntrees}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-alpha-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{alpha} for eight epidemic scenarios. Solid lines and points are
    $R^2$ of tree kernel \gls{kSVR} under various kernel meta-parameters.
    Dashed and dotted lines are $R^2$ of linear regression against Sackin's
    index, and \gls{SVR} using \gls{nltt}.
  }
  \label{fig:alphacrossv}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-I-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{I} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Icrossv}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-m-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{m} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:mcrossv}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-N-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{N} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Ncrossv}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-alpha-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{alpha}, for eight epidemic
    scenarios.
  }
  \label{fig:alphakpca}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-I-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{I}, for eight epidemic
    scenarios.
  }
  \label{fig:Ikpca}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-m-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{m}, for eight epidemic
    scenarios.
  }
  \label{fig:mkpca}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{kernel-N-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{N}, for eight epidemic
    scenarios.
  }
  \label{fig:Nkpca}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{gridsearch-alpha-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{alpha} values. The other \gls{BA} parameters were fixed at \gls{I} =
    1000, \gls{N} = 5000, and \gls{m} = 2. 
  }        
  \label{fig:gridalpha}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{gridsearch-I-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{I} values. The other \gls{BA} parameters were fixed at \gls{alpha} =
    1.0, \gls{N} = 5000, and \gls{m} = 2. 
  }        
  \label{fig:gridI}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{gridsearch-m-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{m} values. The other \gls{BA} parameters were fixed at \gls{alpha} =
    1.0, \gls{I} = 1000, and \gls{N} = 5000.
  }        
  \label{fig:gridm}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{gridsearch-N-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{N} values. The other \gls{BA} parameters were fixed at \gls{alpha} =
    1.0, \gls{I} = 1000, and \gls{m} = 2. 
  }        
  \label{fig:gridN}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{abc-point-estimate-m3.pdf}
  \caption{                                              
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data. Values shown are for
    simulations with \gls{m} = 3. Dashed lines indicate true values. (A)
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held
    fixed in these simulations at the values \gls{m} = 3 and \gls{N} = 5000.
  }        
  \label{fig:abcm3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{abc-point-estimate-m4.pdf}
  \caption{                                              
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data. Values shown are for
    simulations with \gls{m} = 4. Dashed lines indicate true values. (A)
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held
    fixed in these simulations at the values \gls{m} = 4 and \gls{N} = 5000.
  }        
  \label{fig:abcm4}
\end{figure}

\begin{figure}
  \includegraphics{cuevas2009-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{cuevas2009hiv} data. Vertical lines indicate maximum \textit{a
      posteriori} estimates, and shaded areas are 95\% highest posterior
      density intervals. $x$-axis indicates regions of nonzero prior density.
  }
  \label{fig:cuevas}
\end{figure}

\begin{figure}
  \includegraphics{li2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for \textcite{li2015hiv}
      data. Vertical lines indicate maximum \textit{a posteriori} estimates,
      and shaded areas are 95\% highest posterior density intervals. $x$-axis
      indicates regions of nonzero prior density.
  }
  \label{fig:li}
\end{figure}

\begin{figure}
  \includegraphics{niculescu2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{niculescu2015recent} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:niculescu}
\end{figure}

\begin{figure}
  \includegraphics{novitsky2014-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{novitsky2013phylogenetic, novitsky2014impact} data. Vertical
      lines indicate maximum \textit{a posteriori} estimates, and shaded areas
      are 95\% highest posterior density intervals. $x$-axis indicates regions
      of nonzero prior density.
  }
  \label{fig:novitsky}
\end{figure}

\begin{figure}
  \includegraphics{wang2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{wang2015targeting} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:wang}
\end{figure}

<<abc_posterior, echo=FALSE, results="asis">>=
    N <- 5000
    replicate <- 0
    for (m in c(2, 3, 4)) {
    for (I in c(1000, 2000)) {
    for (alpha in c(0, 0.5, 1, 1.5, 2)) {
        fn <- sprintf("abc-posterior/%2f_%d_%d_%d_%d.pdf", alpha, I, m, N, replicate)
        lab <- sprintf("fig:%2f-%d-%d-%d-%d", alpha, I, m, N, replicate)
        cat("\\begin{figure}\n")
        cat("\\centering\n")
        cat("\\includegraphics{", fn, "}\n")
        cat("\\caption{\n")
        cat("Approximate marginal posterior distributions of Barab\\'asi-Albert model parameters obtained using kernel-ABC for one simulated dataset. Dashed lines indicate true values, and shaded areas shown 95\\% highest posterior density intervals.\n")
        cat("}\n")
        cat("\\label{", lab, "}\n")
    }
    }
    }
@

>>>>

\begin{figure}[H]
  \centering
  \includegraphics{kernel-I-tree.pdf}
  \caption{
    Transmission trees simulated over \gls{BA} networks with varying values of
    $I$, the number of infected nodes when the epidemic simulation was stopped.
  }
  \label{fig:Itrees}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-m-tree.pdf}
  \caption{
    Transmission trees simulated over \gls{BA} networks with varying values of
    $m$, the number of edges added per vertex.
  }
  \label{fig:mtrees}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-N-tree.pdf}
  \caption{
    Transmission trees simulated over \gls{BA} networks with varying values of
    $N$, the number of nodes in the network.
  }
  \label{fig:Ntrees}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-alpha-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{alpha} for eigH epidemic scenarios. Solid lines and points are
    $R^2$ of tree kernel \gls{kSVR} under various kernel meta-parameters.
    Dashed and dotted lines are $R^2$ of linear regression against Sackin's
    index, and \gls{SVR} using \gls{nltt}.
  }
  \label{fig:alphacrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-I-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{I} for eigH epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Icrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-m-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{m} for eigH epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:mcrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-N-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{N} for eigH epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Ncrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-alpha-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{alpha}, for eigH epidemic
    scenarios.
  }
  \label{fig:alphakpca}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-I-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{I}, for eigH epidemic
    scenarios.
  }
  \label{fig:Ikpca}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-m-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{m}, for eigH epidemic
    scenarios.
  }
  \label{fig:mkpca}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-N-kpca.pdf}
  \caption{
    Kernel principal components projection of trees simulated under three
    different values of \gls{BA} parameter \gls{N}, for eigH epidemic
    scenarios.
  }
  \label{fig:Nkpca}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-alpha-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{alpha} values. The other \gls{BA} parameters were fixed at \gls{I} =
    1000, \gls{N} = 5000, and \gls{m} = 2. 
  }        
  \label{fig:gridalpha}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-I-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{I} values. The other \gls{BA} parameters were fixed at \gls{alpha} =
    1.0, \gls{N} = 5000, and \gls{m} = 2. 
  }        
  \label{fig:gridI}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-m-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{m} values. The other \gls{BA} parameters were fixed at \gls{alpha} =
    1.0, \gls{I} = 1000, and \gls{N} = 5000.
  }        
  \label{fig:gridm}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-N-kernel.pdf}
  \caption{                                              
    Grid search kernel scores for testing trees simulated under various             
    \gls{N} values. The other \gls{BA} parameters were fixed at \gls{alpha} =
    1.0, \gls{I} = 1000, and \gls{m} = 2. 
  }        
  \label{fig:gridN}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{abc-point-estimate-m3.pdf}
  \caption{                                              
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data. Values shown are for
    simulations with \gls{m} = 3. Dashed lines indicate true values. (A)
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held
    fixed in these simulations at the values \gls{m} = 3 and \gls{N} = 5000.
  }        
  \label{fig:abcm3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{abc-point-estimate-m4.pdf}
  \caption{                                              
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data. Values shown are for
    simulations with \gls{m} = 4. Dashed lines indicate true values. (A)
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held
    fixed in these simulations at the values \gls{m} = 4 and \gls{N} = 5000.
  }        
  \label{fig:abcm4}
\end{figure}

\begin{figure}[H]
  \includegraphics{cuevas2009-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{cuevas2009hiv} data. Vertical lines indicate maximum \textit{a
      posteriori} estimates, and shaded areas are 95\% highest posterior
      density intervals. $x$-axis indicates regions of nonzero prior density.
  }
  \label{fig:cuevas}
\end{figure}

\begin{figure}[H]
  \includegraphics{li2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for \textcite{li2015hiv}
      data. Vertical lines indicate maximum \textit{a posteriori} estimates,
      and shaded areas are 95\% highest posterior density intervals. $x$-axis
      indicates regions of nonzero prior density.
  }
  \label{fig:li}
\end{figure}

\begin{figure}[H]
  \includegraphics{niculescu2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{niculescu2015recent} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:niculescu}
\end{figure}

\begin{figure}[H]
  \includegraphics{novitsky2014-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{novitsky2013phylogenetic, novitsky2014impact} data. Vertical
      lines indicate maximum \textit{a posteriori} estimates, and shaded areas
      are 95\% highest posterior density intervals. $x$-axis indicates regions
      of nonzero prior density.
  }
  \label{fig:novitsky}
\end{figure}

\begin{figure}[H]
  \includegraphics{wang2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{wang2015targeting} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:wang}
\end{figure}

<<abc_posterior, echo=FALSE, results="asis">>=
    N <- 5000
    replicate <- 0
    for (m in c(2, 3, 4)) {
    for (I in c(1000, 2000)) {
    for (alpha in c(0, 0.5, 1, 1.5)) {
        fn <- sprintf("{abc-posterior/%.1f_%d_%d_%d_%d}.pdf", alpha, I, m, N, replicate)
        lab <- sprintf("{fig:%.1f-%d-%d-%d-%d}", alpha, I, m, N, replicate)
        cat("\\begin{figure}[H]\n")
        cat("\\centering\n")
        cat(paste0("\\includegraphics{", fn, "}\n"))
        cat("\\caption{\n")
        cat("Approximate marginal posterior distributions of Barab\\'asi-Albert model parameters obtained using kernel-ABC for one simulated dataset. Dashed lines indicate true values, and shaded areas shown 95\\% highest posterior density intervals.\n")
        cat("}\n")
        cat("\\label{", lab, "}\n")
        cat("\\end{figure}\n")
    }
    }
    }
@
